Cognate beginnings to bilingual lexical acquisition

### 2023-10-03 manuscript/manuscript.qmd
Fix table caption

sum_rows <- function(x) {
    if (is.numeric(x)) {
        sum(x)
    } else if (is.list(x)) {
        ""
    } else {
        "*N*"
    }
}

sums_row <- tbl_data |>
    summarise(
        semantic_category = "*N*",
        across(a:d, sum),
        items = "-"
    )

>>>>

sum_rows <- function(x) {
    if (is.numeric(x)) {
        sum(x)
    } else if (is.list(x)) {
        ""
    } else {
        "N"
    }
}

sums_row <- tbl_data |>
    summarise(
        semantic_category = "N",
        across(a:d, sum),
        items = "-"
    )

### 2023-10-03 manuscript/manuscript.tex
Fix table caption

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, sharp corners, interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

\centering
\begin{tabular}{lccccl}
\toprule
Semantic category & List A & List B & List C & List D & Examples\\
\midrule
Household items & 31 & 26 & 30 & 25 & clock, video\\
Food and drink & 29 & 26 & 23 & 27 & sausage, yogurt\\
Animals & 26 & 23 & 19 & 25 & panther, tiger\\
Outside & 14 & 13 & 13 & 15 & farm, stone\\
Body parts & 14 & 12 & 11 & 11 & face, finger\\
\addlinespace
Toys & 11 & 11 & 12 & 13 & piano, racket\\
Clothes & 12 & 12 & 10 & 10 & zipper, sandal\\
Vehicles & 9 & 10 & 11 & 10 & helicopter, tractor\\
Colours & 6 & 6 & 6 & 6 & red, green\\
People & 7 & 4 & 6 & 6 & police, babysitter\\
\addlinespace
Furniture and rooms & 4 & 4 & 4 & 4 & corridor, terrace\\
Time & 2 & 2 & 2 & 2 & day, night\\
Adventures & 1 & 1 & 1 & 1 & witch\\
Parts of things & 1 & 1 & 1 & 1 & wheel\\
\midrule
*N* & 167 & 151 & 149 & 156 & -\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

\centering
\begin{tabular}{lccccl}
\toprule
Semantic category & List A & List B & List C & List D & Examples\\
\midrule
Household items & 31 & 26 & 30 & 25 & clock, video\\
Food and drink & 29 & 26 & 23 & 27 & sausage, yogurt\\
Animals & 26 & 23 & 19 & 25 & panther, tiger\\
Outside & 14 & 13 & 13 & 15 & farm, stone\\
Body parts & 14 & 12 & 11 & 11 & face, finger\\
\addlinespace
Toys & 11 & 11 & 12 & 13 & piano, racket\\
Clothes & 12 & 12 & 10 & 10 & zipper, sandal\\
Vehicles & 9 & 10 & 11 & 10 & helicopter, tractor\\
Colours & 6 & 6 & 6 & 6 & red, green\\
People & 7 & 4 & 6 & 6 & police, babysitter\\
\addlinespace
Furniture and rooms & 4 & 4 & 4 & 4 & corridor, terrace\\
Time & 2 & 2 & 2 & 2 & day, night\\
Adventures & 1 & 1 & 1 & 1 & witch\\
Parts of things & 1 & 1 & 1 & 1 & wheel\\
\midrule
N & 167 & 151 & 149 & 156 & -\\
\bottomrule
\end{tabular}
\end{table}
